### 2019-02-20 2-Chapters/3-Chapter/chapter3.tex
Done for now, I don't like the content of Chapter 3 at all for now, but at least there is something.

SMPyBandits implements all collision models found in the literature (in the module \texttt{\href{https://SMPyBandits.GitHub.io/docs/Environment.CollisionModels.html}{Environment.CollisionModels}}), as well as all the algorithms from the last 10 years (in the module \texttt{\href{https://SMPyBandits.GitHub.io/docs/Environment.CollisionModels.html}{Environment.CollisionModels}}).
%
It includes
\texttt{rhoRand} (\texttt{\href{https://SMPyBandits.GitHub.io/docs/PoliciesMultiPlayers.rhoRand.html}{PoliciesMultiPlayers.rhoRand}}) from \cite{Anandkumar11},
\texttt{MEGA} (\texttt{\href{https://SMPyBandits.GitHub.io/docs/Policies.MEGA.html}{Policies.MEGA}}) \cite{Avner15},
\texttt{MusicalChair} (\texttt{\href{https://SMPyBandits.GitHub.io/docs/Policies.MusicalChair.html}{Policies.MusicalChair}}) from \cite{Rosenski16},
and our state-of-the-art algorithms
\texttt{RandTopM} (\texttt{\href{https://SMPyBandits.GitHub.io/docs/PoliciesMultiPlayers.RandTopM.html}{PoliciesMultiPlayers.RandTopM}}) and
\texttt{MCTopM} (\texttt{\href{https://SMPyBandits.GitHub.io/docs/PoliciesMultiPlayers.MCTopM.html}{PoliciesMultiPlayers.MCTopM}}) from \cite{Besson2018ALT}.
For comparison, realistic or full-knowledge centralized algorithms are also implemented.

@@

% https://tex.stackexchange.com/a/12430/
\begin{listing}[h!]
    \begin{minted}[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{bash}
# 3. run a single-player simulation
$ BAYES=False ARM_TYPE=Bernoulli N=1000 T=10000 K=9 N_JOBS=4 \
MEANS=[0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9] \
python3 main.py configuration.py
    \end{minted}
    \caption{Small snippet of Bash to run a simple experiment with SMPyBandits}
    % \captionof{listing}{Small snippet of Bash to run a simple experiment with SMPyBandits \label{lst:3:howToRunBasicLibrary}.}
    \label{lst:3:howToRunBasicLibrary}
\end{listing}

@@

% https://tex.stackexchange.com/a/12430/
\begin{listing}[h!]
    \begin{minted}[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{python3}
configuration["policies"] = [
  {"archtype": klUCB, "params": {"klucb": klucbBern}},
  {"archtype": klUCBPlusPlus, "params": {"horizon": HORIZON, "klucb": klucbBern}},
  {"archtype": UCBalpha, "params": {"alpha": 1}},
  {"archtype": Thompson, "params": {"posterior": Beta}}
]
    \end{minted}
    \caption{Small snippet of Python code to configure the list of algorithms tested on a problem.}
    % \captionof{listing}{Small snippet of Python code to configure the list of algorithms tested on a problem. \label{lst:3:howToConfigureAlgorithms}.}
    \label{lst:3:howToConfigureAlgorithms}
\end{listing}

Running the simulation as shown above will save figures in a sub-folder, as well as save data (pulls, rewards and regret) in a HDF5 file (\cite{h5py}, \texttt{\href{http://docs.h5py.org/en/stable/high/file.html}{docs.h5py.org/en/stable/high/file.html}})\footnote{~For example, this simulation produces this HDF5 file \texttt{\href{https://github.com/SMPyBandits/SMPyBandits/blob/master/plots/paper/example.hdf5}{GitHub.com/SMPyBandits/SMPyBandits/blob/master/plots/paper/example.hdf5}}.}.
Figure~\ref{fig:3:firstPlot} below shows the average regret for these $4$ algorithms.
The regret is the difference between the cumulated rewards of the best fixed-armed strategy (which is the oracle strategy for stationary bandits), and the cumulated rewards of the considered algorithms.
The Figure~\ref{fig:3:firstPlot_hist} shows the histogram of regret for the same experiment.

@@

In \cite{Besson2018DoublingTricks}, we used SMPyBandits to illustrate and compare different "doubling trick" schemes\footnote{~See the page \texttt{\href{https://SMPyBandits.GitHub.io/DoublingTrick.html}{SMPyBandits.GitHub.io/DoublingTrick.html}} on the documentation.}. In sequential learning, an algorithm is anytime if it does not need to know the horizon $T$ of the experiments. A well-known trick for transforming any non-anytime algorithm to an anytime variant is the "Doubling Trick": start with an horizon $T_0\in\mathbb{N}^$, and when $t > T_i$, use $T_{i+1} = 2 T_i$. We studied two generic sequences of growing horizons (geometric and exponential), and we proved two theorems that generalized previous results. A geometric sequence suffices to conserve minimax regret bounds (in $R_T = \mathcal{O}(\sqrt{T})$), with a constant multiplicative loss $\ell \leq 4$, but cannot be used to conserve a logarithmic regret bound (in $R_T = \mathcal{O}(\log(T))$). And an exponential sequence can be used to conserve logarithmic bounds, with a constant multiplicative loss also $\ell \leq 4$ in the usual setting. It is still an open question to know if a well-tuned exponential sequence can conserve minimax bounds, or "weak" minimax bounds (in $R_T = \mathcal{O}(\sqrt{T \log(T)})$).

@@

% https://tex.stackexchange.com/a/12430/
% \begin{small}
% \begin{listing}[h!]
    \inputminted[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{python3}{2-Chapters/3-Chapter/src/example_of_use_of_SMPyBandits.py}
    % \caption{Small example of \texttt{main.py} file}
    \captionof{listing}{Example of use of SMPyBandits\label{lst:3:exampleOfUse}.}
    % \label{lst:3:exampleOfUse}
% \end{listing}
% \end{small}

@@

% https://tex.stackexchange.com/a/12430/
% \begin{listing}[h!]
    \inputminted[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{python3}{2-Chapters/3-Chapter/src/example_of_main_singleplayer.py}
    % \caption{Small example of \texttt{main.py} file}
    \captionof{listing}{Small example of \texttt{main.py} file\label{lst:3:main}.}
    % \label{lst:3:main}
% \end{listing}

@@

% https://tex.stackexchange.com/a/12430/
% \begin{listing}[h!]
    \inputminted[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{python3}{2-Chapters/3-Chapter/src/example_of_configuration_singleplayer.py}
    % \caption{Small example of \texttt{configuration.py} file}
    \captionof{listing}{Small example of \texttt{configuration.py} file\label{lst:3:configuration}.}
    % \label{lst:3:configuration}
% \end{listing}

>>>>

SMPyBandits implements all collision models found in the literature (in the module \texttt{\href{https://SMPyBandits.GitHub.io/docs/Environment.CollisionModels.html}{Environment.CollisionModels}}), as well as all the algorithms from the last 10 years (in the module \texttt{\href{https://SMPyBandits.GitHub.io/docs/Environment.CollisionModels.html}{Environment.CollisionModels}}).
%
It includes
\texttt{rhoRand} (\texttt{\href{https://SMPyBandits.GitHub.io/docs/PoliciesMultiPlayers.rhoRand.html}{PoliciesMultiPlayers.rhoRand}}) from \cite{Anandkumar11},
\texttt{MEGA} (\texttt{\href{https://SMPyBandits.GitHub.io/docs/Policies.MEGA.html}{Policies.MEGA}}) from \cite{Avner15},
\texttt{MusicalChair} (\texttt{\href{https://SMPyBandits.GitHub.io/docs/Policies.MusicalChair.html}{Policies.MusicalChair}}) from \cite{Rosenski16},
and our state-of-the-art algorithms
\texttt{RandTopM} (\texttt{\href{https://SMPyBandits.GitHub.io/docs/PoliciesMultiPlayers.RandTopM.html}{PoliciesMultiPlayers.RandTopM}}) and
\texttt{MCTopM} (\texttt{\href{https://SMPyBandits.GitHub.io/docs/PoliciesMultiPlayers.MCTopM.html}{PoliciesMultiPlayers.MCTopM}}) from \cite{Besson2018ALT}.
For comparison, realistic (\eg, \UCB{} for multiple play) or full-knowledge centralized algorithms are also implemented.

@@

% https://tex.stackexchange.com/a/12430/
\begin{small}
\begin{listing}[h!]
    \begin{minted}[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{bash}
# 3. run a single-player simulation
$ BAYES=False ARM_TYPE=Bernoulli N=1000 T=10000 K=9 N_JOBS=4 \
MEANS=[0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9] \
python3 main.py configuration.py
    \end{minted}
    \caption{Small snippet of Bash to run a simple experiment with SMPyBandits}
    % \captionof{listing}{Small snippet of Bash to run a simple experiment with SMPyBandits \label{lst:3:howToRunBasicLibrary}.}
    \label{lst:3:howToRunBasicLibrary}
\end{listing}
\end{small}

@@

% https://tex.stackexchange.com/a/12430/
\begin{small}
\begin{listing}[h!]
    \begin{minted}[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{python3}
configuration["policies"] = [
  {"archtype": klUCB, "params": {"klucb": klucbBern}},
  {"archtype": klUCBPlusPlus, "params": {"horizon": HORIZON, "klucb": klucbBern}},
  {"archtype": UCBalpha, "params": {"alpha": 1}},
  {"archtype": Thompson, "params": {"posterior": Beta}}
]
    \end{minted}
    \caption{Small snippet of Python code to configure the list of algorithms tested on a problem.}
    % \captionof{listing}{Small snippet of Python code to configure the list of algorithms tested on a problem. \label{lst:3:howToConfigureAlgorithms}.}
    \label{lst:3:howToConfigureAlgorithms}
\end{listing}
\end{small}

Running the simulation as shown above will save figures in a sub-folder, as well as save data (pulls, rewards and regret) in a HDF5 file (\cite{h5py}, \texttt{\href{http://docs.h5py.org/en/stable/high/file.html}{docs.h5py.org/en/stable/high/file.html}})\footnote{~For example, this simulation produces this HDF5 file\\\texttt{\href{https://github.com/SMPyBandits/SMPyBandits/blob/master/plots/paper/example.hdf5}{GitHub.com/SMPyBandits/SMPyBandits/blob/master/plots/paper/example.hdf5}}}.
Figure~\ref{fig:3:firstPlot} below shows the average regret for these $4$ algorithms.
The regret is the difference between the cumulated rewards of the best fixed-armed strategy (which is the oracle strategy for stationary bandits), and the cumulated rewards of the considered algorithms.
The Figure~\ref{fig:3:firstPlot_hist} shows the histogram of regret for the same experiment.

@@

In \cite{Besson2018DoublingTricks}, we used SMPyBandits to illustrate and compare different "doubling trick" schemes\footnote{~See the page \texttt{\href{https://SMPyBandits.GitHub.io/DoublingTrick.html}{SMPyBandits.GitHub.io/DoublingTrick.html}} on the documentation.}. In sequential learning, an algorithm is anytime if it does not need to know the horizon $T$ of the experiments. A well-known trick for transforming any non-anytime algorithm to an anytime variant is the ``Doubling Trick'': start with an horizon $T_0\in\mathbb{N}^*$, and when $t > T_i$, use $T_{i+1} = 2 T_i$. We studied two generic sequences of growing horizons (geometric and exponential), and we proved two theorems that generalized previous results. A geometric sequence suffices to conserve minimax regret bounds (in $R_T = \mathcal{O}(\sqrt{T})$), with a constant multiplicative loss $\ell \leq 4$, but cannot be used to conserve a logarithmic regret bound (in $R_T = \mathcal{O}(\log(T))$). And an exponential sequence can be used to conserve logarithmic bounds, with a constant multiplicative loss also $\ell \leq 4$ in the usual setting. It is still an open question to know if a well-tuned exponential sequence can conserve minimax bounds, or "weak" minimax bounds (in $R_T = \mathcal{O}(\sqrt{T \log(T)})$).

@@

% https://tex.stackexchange.com/a/12430/
\begin{small}
% \begin{listing}[h!]
    \inputminted[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{python3}{2-Chapters/3-Chapter/src/example_of_use_of_SMPyBandits.py}
    % \caption{Small example of \texttt{main.py} file}
    \captionof{listing}{Example of use of SMPyBandits\label{lst:3:exampleOfUse}.}
    % \label{lst:3:exampleOfUse}
% \end{listing}
\end{small}

@@

% https://tex.stackexchange.com/a/12430/
\begin{small}
% \begin{listing}[h!]
    \inputminted[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{python3}{2-Chapters/3-Chapter/src/example_of_main_singleplayer.py}
    % \caption{Small example of \texttt{main.py} file}
    \captionof{listing}{Small example of \texttt{main.py} file\label{lst:3:main}.}
    % \label{lst:3:main}
% \end{listing}
\end{small}

@@

% https://tex.stackexchange.com/a/12430/
\begin{small}
% \begin{listing}[h!]
    \inputminted[linenos=true,numbersep=5pt,frame=lines,framesep=2mm]{python3}{2-Chapters/3-Chapter/src/example_of_configuration_singleplayer.py}
    % \caption{Small example of \texttt{configuration.py} file}
    \captionof{listing}{Small example of \texttt{configuration.py} file\label{lst:3:configuration}.}
    % \label{lst:3:configuration}
% \end{listing}
\end{small}
